### 2019-10-25 paper/introduction.tex

\section{Introduction} \label{Introduction}
The \gls{GIF} defines eight technological goals for the next generation
nuclear systems. These goals are defined in four broad areas: safety and reliability, non-proliferation and physical protection, economics, and sustainability \cite{doe2002technology}. The \gls{MSR} has many advantages that agree
with \gls{GIF}'s goals, like: liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy, and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected the \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl);
this liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows fission heat to transfer from the reactor
core to intermediate heat exchanger.

>>>>

\section{Introduction} \label{Introduction}
The \gls{GIF} defines eight technological goals for the next generation
nuclear systems. These goals are defined in four broad areas: safety and reliability, non-proliferation and physical protection, economics, and sustainability \cite{doe2002technology}. The \gls{MSR} has many advantages that agree
with \gls{GIF}'s goals, like: liquid fuel, inherent safety, online
reprocessing and refueling, excellent neutron economy, and operation near
atmospheric
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
Thus, the \gls{GIF} selected the \gls{MSR} as one of the promising Generation-IV
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl);
this liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
circulates through the core and allows fission heat to transfer from the reactor
core to intermediate heat exchangers.
